---
title: "Extract Data"
output: html_notebook
---

Using ML to predict the dpw using UK bio-bank 

## Load the libraries

```{r}
library(data.table)
library(tidyverse)
library(caret)
library(caretEnsemble)
```
## Extract random 2000 participants from UK BioBank 

```{r}
famdata <- fread("")
dim(famdata)
data_sam <- sample(1:nrow(famdata), 2000)
famdata2 <- famdata[data_sam,]
write.table(famdata[,c(1,2)], "", row.names = F, quote = F)
```

Extract SNPs with certain P-value threshold (10e4, 10e5, 10e6)

```{r}
snp_path <-"" 
snp_df <- snp_fun(snp_path, P-Value = 0.00001)
write.table(snp_df, "", row.names = F, quote = F)
```

Use plink to extract the genetic data of these particiants and convert it to raw data

```{bash}
sudo ~/plink/plink/plink --bfile ~/UKB/download/ukb_non_imputed_best_guess_noQC --keep ~/UKB_2/graLD_sample_500.txt --make-bed --out ~/UKB/download/GraBLD/ukb_graBLD_sample
```

Use plink to extract the genetic material in the identified p-value threshold from the 2000 participants

```{bash}
sudo ~/plink/plink/plink --bfile ukb_graBLD_sample --extract snp_list.txt --make-bed --out ukb_graBLD_sample_e103
```

Convert the binary to raw files (text files), so it could be read in R or Python

```{bash}
sudo ~/plink/plink/plink --bfile /home/ubuntu/UKB/download/GraBLD/ukb_graBLD_sample_2000_e106  --recodeA --out ~/UKB/download/GraBLD/ukb_graBLD_sample_raw_2000_e106
```

