---
title: "R Notebook"
output: html_notebook
---

Applying the ML model to predict drinks per week.

## Load Libraries

```{r}
set.seed(1234)

library(caret)
library(tidyverse)
library(knitr) 
library(data.table)
library(glmnet)
library(caretEnsemble)
library(mlr)

source("100_functions")
```

## Read the Data

```{r}
path <- getwd()
raw_data <- fread(paste0(path,
                    "/ukb_graBLD_sample_raw_2000_e105.raw"))

pheno <- fread(paste0(path,
                      "/all_dpw_covarites_half_million"))
```

## obtain the phenotype:

The phenotype is drinks per week, calculated by counting the number of drinks per week (e.g. beers, spirits, wine, etc).

```{r}
head(pheno)
alc_col <- c("wine","champ",
             "beer", "spirits", 
             "whitewine", "others")

pheno$pheno_dpw <- log(apply(
  pheno[, alc_col], 1, sum) + 1)
```

Extract only the necessary predictors, such as sex, age, weight, height and age squared. And merge the snps with the demographics

```{r}
pheno2 <- pheno[,c("FID","PC1","PC2","PC3","PC4",
                   "PC5","PC6","PC7","PC8",
                   "PC9","PC10","all2","sex",
                   "age_age","weight","height")]

snp_data <- merge(snp_data, pheno3, 
                  by.x = "FID", by.y = "FID")
```

Impute the missing values in the genetic data using the median.

```{r}
colnames(snp_data)[1:10]
## remove some unspecific predictors
dataset_final <- snp_data[,-c(1,2,3,4,5,6)]
dataset_final[1:5,1:10]

imp = mlr::impute(dataset_final, 
                  classes = 
                    list(numeric = imputeMedian(), 
                         integer = imputeMedian(), 
                         factor = imputeMode()))


dataset_final <- imp$data
dataset_final$Phenotype_dpw <- dataset_final$pheno_dpw
dataset_final$pheno_dpw <- NULL
dim(dataset_final)
```

Perform some feature manipulation such as normalization and remve highly correlated features.

```{r}
dataset_final <- trainfun(dataset_final, 
                          target = "pheno_dpw")
```


